Discussion Draft

### 2020-04-15 doc/Discussion.rmd
small changes, spell check

@@

# typical landscape is conserved -- sexually dimorphic meiotic trait (Sardell)

# models

@@

#*caveats: Type II crossovers not accounted for and chromatid interference effects on (multi-crossover chromsomes) could alter the sister cohesion pattern.

# consequences of conserved typical landscape
# most exceptions to the typical landscape, marsupials (pig and tomoato)

#sardel kirkptarick -

# diviation from uniform is due to male rec landscape
# patterns of Fst (Hanel et al, but see Kartej?)
# source could be DSB formation along chromosome - and /or biases in DSB repair 
#CO suppresion, elevated DSB (most repaired as NCO) -- elevated DsB (Brick)

@@

>>>>

other COM, / nucleus membrane citations (Harper, Golubovskaya, & Cande, 2004; Naranjo & Corredor, 2008; Scherthan et al., 1996; Zickler & Kleckner, 2016).

telomere guided movements  citations: (Bass et al.,
2000; Chacon, Delivani, & Tolic, 2016; Curtis, Lukaszewski, & Chrzastek, 1991; Ding, Yamamoto, Haraguchi, & Hiraoka, 2004; Gerton &
Hawley, 2005; Lee, Conrad, & Dresser, 2012; Lefrancois, Rockmill,
Xie, Roeder, & Snyder, 2016; Page & Hawley, 2003)

Repair of DSB - CO
(Anderson & Stack, 2005; Bass et al., 2000; Brown et al., 2005; Croft & Jones, 1989; Higgins, Osman, Jones, & Franklin, 2014; Klutstein & Cooper, 2014, Lukaszewski, 1997; Pratto et al., 2014; Viera, Santos, & Rufas, 2009;
Xiang, Miller, Ross, Alvarado, & Hawley, 2014).

@@

@@

#0. we find the conserved pattern of the typical landscape 
#this trait is a highly conserved aspect of heterochiasmy 
#the exceptions include marsupials which form sex chromosome chains during meiosis -- indicating a potential change to the meiotic program (functional selection)
#it's not known if a similar -- evolutionary force in the other exceptions to the typical landscape, pig and tomatoe.

#regaurdless
#As reviewed in sardel kirkptarick - diviation for a uniform background is generally due to the male recombination landscape.

# these pattern due to (different recombination landscapes along chromosomes can have an impact on the pattern of Fst (Hanel et al 2018)
# additionally other patterns of nucleotide and recombination rates could vary across

#co rate defines the physical scale of linked selection around a locus

# evolutionary genomics from the broad scale heterogenity
#linked selection, (maynarid smith and haig 1974)
#background selection (only with negtive allele), genetic draft (for positive selective mutations)
#gene flow barrier (directional selection is keeping two populations from merging)
# patterns of Fst (Hanel et al, but see Kartej?)

#

# source could be DSB formation along chromosome - and /or biases in DSB repair

#CO suppresion, elevated DSB (most repaired as NCO) -- elevated DsB (Brick)

@@

(also outlined in Hanel et al 2018 -- which connects to typical landscape)
